GEE models

### 2017-10-16 doc/manuscript.Rmd
limitation of outcomes as estimates

Finally, our cohort consists of individuals at-risk for diabetes, 
who are primarily female and European-ancestry and, while sex and ethnicity did
not influence the results presented from this cohort, our findings may not
entirely be generalisable to other populations. However, given these
limitations, our study also has several strengths, including the longitudinal
design and the rigorous statistical techniques and methods applied, which are
specifically suited to investigating temporal relationships and to handling the
multivariate nature of the data. Lastly, our cohort contains highly detailed and
comprehensive variable measurements at each collection visit, and has both
concentration and mol% data for the fatty acids.

>>>>

We used indices of insulin sensitivity and beta cell function estimated from
glucose and insulin values and as such could that lead to measurement bias.
While these indices have all been validated against gold standard measures,
it is possible our measures are not sensitivity enough to identify potential
associations with NEFA.
Finally, our cohort consists of individuals at-risk for diabetes,
who are primarily female and European-ancestry and, while sex and ethnicity did
not influence the results presented from this cohort, our findings may not
entirely be generalisable to other populations. However, given these
limitations, our study also has several strengths, including the longitudinal
design and the rigorous statistical techniques and methods applied, which are
specifically suited to investigating temporal relationships and to handling the
multivariate nature of the data. Lastly, our cohort contains highly detailed and
comprehensive variable measurements at each collection visit, and has both
concentration and mol% data for the fatty acids.
